A UK Case Study on\\Cybersecurity Education and Accreditation

### 2019-07-18 FIE2019-final.tex
Added ack to IoC

The recommendation in \cite[p. 98]{ACM2013a} that cybersecurity be taught largely through other Knowledge Areas is, in abstract, a good idea.  However, in the current state of education resources (sections \S\ref{sec:EDResource})  may be a counsel caution in this approach.  It is more important that issues like SQL injection \cite{Drop2019} or correct use of SSL/TLS \cite{Chenetal2019a} be taught somewhere than that they not be taught at all.
Nevertheless, it is wrong for a complete curriculum to ignore cybersecurity issues for example
\begin{itemize}
	\item teach SQL without teaching SQL Injection~\cite{Drop2019};
	\item teach ``web programming'' without teaching Cross-Site Scripting \cite[(XSS)]{OWASP2017a};
	\item ignore the  impact of GDPR upon systems development;
	\item uncritically teach the use of Agile Development to develop secure systems.
\end{itemize}
\par
The BCS-identified good practice of exploring cybersecurity via a project referencing Industry Standards, possibly PCI DSS, is commended (\S\ref{sec:PCIDSS}).

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager at BCS, The Chartered Institute for IT for supplying the summary information related to accreditation of UK degree programmes. Many people, accreditors and accredited, have contributed to improving the standard of cybersecurity teaching in the UK, and spreading good practice.
\par
{\emph{N.B.}} The first two authors are current Vice-Presidents of BCS, The Chartered Institute for IT, and the third and fourth are past and present Chairs of the BCS Academic Accreditation Committee, providing significant personal insight into the UK's national accreditation policy and procedures.

>>>>

The recommendation in \cite[p. 98]{ACM2013a} that cybersecurity be taught largely through other Knowledge Areas is, in abstract, a good idea.  However, in the current state of education resources (sections \S\ref{sec:EDResource})  may be a counsel caution in this approach.  It is more important that issues like SQL injection \cite{Drop2019} or correct use of SSL/TLS \cite{Chenetal2019a} be taught somewhere than that they not be taught at all.
Nevertheless, it is wrong for a complete curriculum to ignore cybersecurity issues for example:
\begin{itemize}
	\item teach SQL without teaching SQL Injection~\cite{Drop2019};
	\item teach ``web programming'' without teaching Cross-Site Scripting \cite[(XSS)]{OWASP2017a};
	\item ignore the  impact of GDPR upon systems development;
	\item uncritically teach the use of Agile Development to develop secure systems.
\end{itemize}
\par
The BCS-identified good practice of exploring cybersecurity via a project referencing Industry Standards, possibly PCI DSS, is commended (\S\ref{sec:PCIDSS}).

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager at BCS, The Chartered Institute for IT for supplying the summary information related to accreditation of UK degree programmes. Many people, accreditors and accredited, have contributed to improving the standard of cybersecurity teaching in the UK, and spreading good practice.  All authors' institutions are members of the Institute of Coding (\url{https://instituteofcoding.org/}), an initiative funded by the Office for Students (England) and the Higher Education Funding Council for Wales.
\par
{\emph{N.B.}} The first two authors are current Vice-Presidents of BCS, The Chartered Institute for IT, and the third and fourth are past and present Chairs of the BCS Academic Accreditation Committee, providing significant personal insight into the UK's national accreditation policy and procedures.
